\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2014-01-01 paper/paper.tex
More clarifications

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The identification of an apparent limitation in Elm's hover detection
  library, solved by a non-trivial usage pattern that does not require
  modifications to the Elm compiler or runtime, and that generalizes to
  other functions in \texttt{Graphics.Input}.
\item
  An implementation of desktop-style menu in Elm, which incorporates
  several noteworthy ``tricks'' as well as general style best practices.
\item
  An analysis of TodoFRP, the current state-of-the-art in dynamic Elm
  GUIs. We demonstrate how it operates in the absence of our technique,
  and how it could operate in its presence.
\end{itemize}

@@

We have implemented all of this without language modifications. However,
it is hoped that as the community becomes more familiar with functional
GUIs, new libraries are added to incorporate some of our tricks, or even
make them unnecessary. Elm's upcoming third-party library sharing system
looks to be an excellent opportunity to refine abstractions and idioms
for GUIs.

>>>>

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The identification of an apparent limitation in Elm's hover detection
  library, solved by a non-trivial usage pattern that does not require
  modifications to the Elm compiler or runtime, and that generalizes to
  other functions in \texttt{Graphics.Input}. Concretely, this is the
  implementation of \texttt{hoverableJoin}.
\item
  An implementation of desktop-style menus in Elm, which incorporates
  several noteworthy ``tricks'' as well as general style best practices.
\item
  An analysis of TodoFRP, the current state-of-the-art in dynamic Elm
  GUIs. We demonstrate how it operates in the absence of our technique,
  and how it could operate in its presence.
\end{itemize}

@@

We have implemented all of this without language modifications. However,
it is hoped that as the community becomes more familiar with functional
GUIs, new libraries are added that incorporate some of our tricks, or even
make them unnecessary. Elm's upcoming third-party library sharing system
looks to be an excellent opportunity to refine abstractions and idioms
for GUIs.
